---
title: "Figure S1"
output: html_document
---
This notebook contains the code to generate figure panels for Figure S1 in Ahler et al., A Combined Approach Reveals a Regulatory Mechanism Coupling Src’s Kinase Activity, Localization,and Phosphotransferase-Independent Functions, Molecular Cell (2019), https://doi.org/10.1016/j.molcel.2019.02.003. The default ggplot axes labels and text have been hidden and were manually added in later in with graphics software to conform to publishing font size.

Load all required packages
```{r}
require(tidyverse)
require(cowplot)
require(hexbin)
require(reshape2)
require(gridExtra)
require(RColorBrewer)

```


S1B: Bar plot showing the breakdown of the Src mutant library.
```{r}
df_S2B <- read_tsv("Data/Figure S1 Data/2I Data.csv", col_names = TRUE)

p_S2B <- ggplot(df_S2B, aes(x=Group.1, y=sequence_frequency)) + geom_bar(stat="identity", fill = "black") + 
   theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none")  + scale_y_continuous(breaks = c(0,.25,.5,.75,1), limits = c(0,1))
p_S2B

ggsave("S2B.pdf", p_S2B, path = "~/Dropbox/Combined Src Manuscript/Figures/Figure 2/Figure 2 Code/Figure 2 Output/", height = 1.5, width =2.8, units = "in", dpi=500) 



````

S2C: Bar plot showing average activity score of mutations based on amino acid type. B&W

```{r}
df_S2C <- read_tsv("~/Dropbox/Combined Src Manuscript/Figures/Figure 2/Figure 2 Data/Figure 2 Dataframes/S2C Data.tsv", col_names = TRUE)

p_S2C <- ggplot(df_S2C, aes(x=mutant, y=Activity)) + geom_bar(stat="identity", fill = "black") + 
   theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none") 
p_S2C

ggsave("S2C.pdf", p_S2C, path = "~/Dropbox/Combined Src Manuscript/Figures/Figure 2/Figure 2 Code/Figure 2 Output/", height = 1.5, width =2.8, units = "in", dpi=500) 

````

S2D: Scatter plot showing evolutionary conservation plotted against activity score. B&W
```{r}
df_S2D <- read_tsv("~/Dropbox/Combined Src Manuscript/Figures/Figure 2/Figure 2 Data/Figure 2 Dataframes/S2D Data.tsv", col_names = TRUE)

p_S2D <- ggplot(df_S2D, aes(x=normalized_conservation, y=avg_activity)) + geom_point(color = "black") + 
   theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none") 
p_S2D
 
cor.test(df_S2D$normalized_conservation ,df_S2D$avg_activity, method = "pearson") #-0.4851044 
cor.test(df_S2D$normalized_conservation ,df_S2D$avg_activity, method = "spearman") #-0.5555609 




ggsave("S2D.pdf", p_S2D, path = "~/Dropbox/Combined Src Manuscript/Figures/Figure 2/Figure 2 Code/Figure 2 Output/", height = 1.5, width =2.8, units = "in", dpi=500) 

```

