---
title: "Figure 2"
output: html_document
---
This notebook contains the code to generate figure panels for Figure 2 in Ahler et al., A Combined Approach Reveals a Regulatory Mechanism Coupling Src’s Kinase Activity, Localization,and Phosphotransferase-Independent Functions, Molecular Cell (2019), https://doi.org/10.1016/j.molcel.2019.02.003. The default ggplot axes labels and text have been hidden and were manually added in later in with graphics software to conform to publishing font. To see axes labels, comment out the 'theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none")' lines.

Load all required packages
```{r}
require(tidyverse)
require(cowplot)
require(hexbin)
require(reshape2)
require(gridExtra)
require(RColorBrewer)

```


2B: Dot plot showing growth rates of control Src variants in yeast strain.  
```{r}
df_2B <- read_csv("Data/Figure 2 Data/2B Data.csv", col_names = TRUE)
p_2B <- ggplot(df_2B, aes(x=Strain, y=GrowthRate)) + geom_jitter(size=1.5, height=0,width=.4) + stat_summary(fun.y = "mean", geom = "point", pch = "_", size = 16)  +xlim(c("Empty","WT","K298M","T341I"))  + scale_y_continuous(breaks = c(0,0.00064,0.00128,0.00192,0.00256,0.0032), limits = c(0,0.0032)) + theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none")
p_2B

ggsave("2B.pdf", p_2B, path = "Output/Figure 2 Output/", height = 1.5, width =1.8, units = "in", dpi=500)
```


2D: Scatter plot showing activity score correlation between two independent transformations of Src library.
```{r}
#Load independent transformation replicate data
rep1 <- read_tsv("Data/Figure 2 Data/2D_rep1.tsv")

rep2 <- read_tsv("Data/Figure 2 Data/2D_rep2.tsv")

#Convert 'score' to 'activity'
rep1 <- mutate(rep1, Activity = -(score))
rep2 <- mutate(rep2, Activity = -(score))
colnames(rep1)[1] <- "variant"
colnames(rep2)[1] <- "variant"


#Merge to look at activity correlations
Merge <- inner_join(rep1, rep2, by = "variant")

#Select only activity scores
Merge <- select(Merge, variant, Activity.x, Activity.y)

cor(Merge$Activity.x, Merge$Activity.y, method = "pearson") # R = 0.9076656 Pearsons. 
cor(Merge$Activity.x, Merge$Activity.y, method = "spearman") # R = 0.9220022 Spearman. 
ggplot(Merge, aes(x=Activity.x, y=Activity.y)) + geom_point(alpha=1/2, colour = "black", size = 2) + 
  theme(panel.background = element_rect(fill = "white"), panel.border = element_blank(), text = element_text(size=28), axis.text = element_text(colour="black", size=22), axis.line = element_line(color='black', size = 2)) + labs(x = "Activity Score Replicate 1", y = "Activity Score Replicate 2")

#Plot as a geom_hex
hex <- ggplot(Merge, aes(Activity.x, y=Activity.y)) + geom_hex(color="black", bins = 50) + theme(panel.background = element_rect(fill = "white"), panel.border = element_blank(), text = element_text(size=10), axis.text = element_text(colour="black", size=8), axis.line = element_line(color='black', size = 3), legend.position = c(.85,.15), legend.direction = "horizontal", legend.text=element_text(size=8)) + labs(x = "Replicate 1", y = "Replicate 2") + scale_fill_gradient(name = "Count",low = "grey80", high="black")
hex
ggsave("2D.pdf", hex, path = "Output/Figure 2 Output/", height = 2, width =2, units = "in", dpi=500)

```

2E: Dotplot for Activity Score classification
```{r}
df_2E <- read_csv("Data/Figure 2 Data/2E Data.csv")
sum(table(df_2E$Classification)) #n = 3372
table(df_2E$Classification)# gof = 403 12.0%, lof = 1681 49.8%, neutral = 1288 38.2%
col = c("#268450","#1074B2","#DF8634") #set color pallete

p_2E <- ggplot(df_2E, aes(x=Classification, y=df_2E$`Activity Score`, colour = factor(Classification))) + geom_jitter(width=0.4,alpha= 1/5,size=.75) + theme(panel.background = element_rect(fill = "white"), panel.border = element_blank(),axis.line = element_line(color='black', size = 1), legend.position = "none", axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank()) + scale_colour_manual(values = col) + scale_x_discrete( limits=c("loss of function", "neutral", "gain of function"))
p_2E

ggsave("2E.pdf", p_2E, path = "Output/Figure 2 Output/", height = 1.5, width =1.4, units = "in", dpi=300)

```

2G: Dot plot showing growth rates of Src panel variants. 
``` {r}
df_2G <- read_csv("Data/Figure 2 Data/2G Data.csv", col_names = TRUE)
p_2G <- ggplot(df_2G, aes(x=Strain, y=Growth)) + geom_jitter(size=1.5, height=0,width=.12) + stat_summary(fun.y = "mean", geom = "point", pch = "_", size = 16)  +xlim(c("N471Y","P491G","G398T","V274A","E381T","WT","K298M","T341I")) + theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none") + scale_y_continuous(breaks = c(0,0.00064,0.00128,0.00192,0.00256,0.0032), limits = c(0,0.0032))
p_2G

activity_2G <- c(-1.3,-0.9,0,1.9,3.4,0,-1.6,2.5) #activity scores of the select variants, manually pulled from 2E Data.csv in the order as above
aggregate(df_2G$Growth, list(df_2G$Strain), mean) #grabs mean growth rate for each strain
strain_2G <- c(0.002821667, 0.002633333, 0.001968333, 0.001365000,0.000090000,0.0017633333,0.0030366667,0.0001466667) #manually entered from previous line of code
corr_df_2G <- cbind(activity_2G, strain_2G)
corr_df_2G <- as.data.frame(corr_df_2G)
cor.test(corr_df_2G$activity_2G,corr_df_2G$strain_2G, method = "pearson") #-0.9742406  

ggsave("2G.pdf", p_2G, path = "Output/Figure 2 Output/", height = 1.5, width =3.6, units = "in", dpi=500)
```

2I: Dot plot comparing yeast activity scores vs. mammalian cell westerns.
```{r}
df_2I <- read_csv("Data/Figure 2 Data/2I Data.csv", col_names = TRUE)
p_2I <- ggplot(df_2I, aes(x=ActivityScore, y=pTyr)) + geom_jitter(size=1.5, height=0,width=.12) + stat_summary(fun.y = "mean", geom = "point", pch = "_", size = 16) + theme(axis.text=element_blank(),axis.title=element_blank(),legend.position = "none") 
p_2I

cor.test(df_2I$ActivityScore,df_2I$pTyr, method = "pearson") #0.9688707 


ggsave("2I.pdf", p_2I, path = "Output/Figure 2 Output/", height = 1.5, width =2.6, units = "in", dpi=500)
```